\beginsong{Of Human Bondage}[by={Other Lies}]

  \lilypondfile[nofragment]{intro.ly}

  \chordsoff
  \beginverse
  Will I always wander
  Like a stranger to the world?
  Watching the idiots in the parks
  Of some satellite town
  Violent red and Carmine kisses,
  Where the hell did all of this disappear?
  I am falling off the edge
  \endverse
  
  \beginchorus
  \lilypondfile[nofragment]{chorus.ly}
  And where,
  Where the hell am I falling in?
  I should have turned away,
  It smells the end on tortures hill
  Am I just fading away?
  Am I my own king,
  Bouncing down the stairs?
  \endchorus
  
  \textnote{Solo}
  
  \beginverse
  I would do almost anything
  To escape this obscene life,
  And believe in some lies like
  "somewhere else is a better place"
  Flooded in drinks like in a war crime,
  Is this where my youth disappeared?
  All I fear is to forget
  \endverse

  \beginchorus
  Please now
  Say those words I love to hear,
  I am writhing in pain,
  It smells like death on tortures hill
  Can you rescue me from there?
  With just a kiss?
  I'd feel like a prince in your eyes
  \endchorus

  \beginverse
  \textnote{Bridge}
  \lilypondfile[nofragment]{bridge.ly}
  
  There was no clear reason to end up like this,
  Is there a good reason to loose myself at all?
  If only I could be some millions light years away,
  If only I could seize up your white hands
  There is no way to get away from here,
  Has anyone seen it done before?
  If I only I could not feel so sick of it,
  I would not have to howl like this
  If only I could be that priceless in your eyes  
  \endverse

  \textnote{Outro}
  \lilypondfile[nofragment]{outro.ly}
  
\endsong
