%% A4
\documentclass[12pt]{article}
\usepackage[a4paper,margin=2cm]{geometry}

%% Tablet
%% \documentclass[10pt]{article}
%% \usepackage[paperwidth=441pt,paperheight=666pt,margin=8mm,footskip=15mm]{geometry}

%% Phone
%% \documentclass[14pt]{article}
%% \usepackage[a6paper,margin=3mm]{geometry}

\usepackage[chorded,noscripture]{songs}
\usepackage{lyluatex}

\usepackage{array}
\usepackage[table]{xcolor}

\indexeson
\newindex{mainindex}{idxfile}
%%\newauthorindex{authidx}{authfile}

\renewcommand{\everychorus}{\textnote{Chorus:}}
%%\setlength{\cbarwidth}{0pt}
%%\setlength{\sbarheight}{0pt}

\songcolumns{2}
\renewcommand{\lyricfont}{\sffamily\small}
\renewcommand{\printchord}[1]{\rmfamily\bf#1}

%%\noversenumbers

\title{Mercy Song Book}
\author{Dimitri}

\begin{document}

\showindex[2]{Other Lies Song Book}{mainindex}

\begin{songs}{}

  \beginsong{Bones}[by={Other Lies}]
  \lilypondfile{Bones.ly}  
  \beginverse
  \[Em] I never quite \[B]felt
  The dif\[A]ference between the \[G]right and wrong
  \[Em] I never quite \[B]knew
  The \[A]limits I should \[G]not go beyond
  \[Em] I never quite \[B]knew
  My\[A]self at \[G]all
  \endverse
  \beginchorus
  \lilypondfile{Bones-Chorus-1.ly}  
  Now I can feel it in my bones,
  I really know where I belong
  With my naked soul in front of all,
  I know where I went wrong
  \endchorus
  \beginverse
  For sure I mistook
  The empty places for a royal court
  And my small steps for great endeavours
  And I just confused my mess with the complex
  Smothered by the tides of my pride
  \endverse
  \beginchorus
  \lilypondfile{Bones-Chorus-2.ly}  
  Now I can feel it in my bones,
  Have to confess I lost control
  Now my body is lost for good for all
  But I know where I went wrong \rep{2}
  \endchorus
  \textnote{Solo}
  \beginchorus
  Now I can feel it in my bones,
  This holy fire burns my soul!
  Pulverized by some unknown forces,
  I know where I went wrong \rep{2}
  \endchorus
  \endsong

  \beginsong{Gin Lane}[by={Other Lies}]
  \textnote{Intro}  
  \lilypondfile{GinLane-Intro.ly}
  \beginverse
  Well I wear this purity ring
  And I have seen now where the edges are
  Like in those boring dreams
  When you run after a thing,
  You just can't never catch
  Why didn't I give it up before I start?
  Why didn't I stop it just before it hurts?
  Is there anywhere else to go now?
  Is there anything else to do now?
  \endverse
  \beginchorus
  \lilypondfile{GinLane-Chorus.ly}
  Will all of this be such in vain?
  Do I always have to be that lame?
  Will I always be just like this?
  Is it always the same?
  \endchorus
  \beginverse
  Now you are getting undressed
  I smell your skin and kiss your neck
  I paid for it and as you are getting higher
  My feeling is just getting stronger and stronger
  Why didn't I kill it before it grows ?
  What I am waiting from you now?
  I really should have known it before
  Do you really have to leave me now?
  \endverse
  \beginchorus
  Will all of this always be such in vain?
  Are you trying to fool me again?
  Are you lurking in the shade of my death?
  Is it the way I try to fool myself?
  \endchorus
  \textnote{Bridge}  
  \lilypondfile{GinLane-Bridge.ly}
  \beginverse  
  No matter hard I try,
  you are out of reach
  You are the end of the line,
  You're the devil that whispers the kindest words  
  \endverse
  \textnote{Solo}
  \lilypondfile{GinLane-Solo.ly}
  \endsong

 \end{songs}
\end{document}
